### 2014-03-14 src/methodology.Rnw
updates: methodology related
For related: got the message, for methodology, fixed
the problems pointed out.

\section{Methodology} \label{sec:methodology} Our selection of
programs was driven by a few overriding concerns. Our primary
requirement was that our results had to be as widely applicable as
possible for real-world programs. Secondly, we strived for a
statistically significant result, reducing the number of variables
present in the experiments. For this reason we chose a random sample
of Java projects from Github\cite{github} that use the popular
maven\cite{maven} build system, following the methodology used by some
of the authors in an ICSE 2014 paper~\cite{gopinath2014code}. As in
that work, we utilize two kinds of of test suites: the original test
suites present in a limited number of projects, and automatically
generated test suites from Randoop~\cite{randoop}.  Due to limited resources, we had to
further reduce the programs and test suites to those that could finish
mutation analysis in 10 minutes. From this set of test suites, we
sampled 110 suites each for both original and randoop generated
test suites. This gave us 81 unique projects for both original and
Randoop suites, and remaining projects having both flavors of test suites. {\bf ADG I have no idea what that last sentence means, really.}

@@

We next extended this approach to sample from each method instead, but
used the number of lines in the method as the number of mutants to be
sampled from it. This provided a test of the hypothesis of how
important a mutation samplings relationship to simple code coverage
was. This was extended to class and project scope also.

For the first variant, we applied the x\% sampling to the result of the first
sampling based on line counts. That is, in the case of methods, we first
selected \textit{linecount} mutants each from each method, and applied the x\%
selection to the result of this selection. For the second variant, we did
the sampling in one go, where we chose \textit{linecount/x} number of mutants from
each program element. {\bf ADG:  Could maybe make this clearer?}

>>>>

\section{Methodology} \label{sec:methodology} Our selection of
programs was driven by a few overriding concerns. Our primary
requirement was that our results had to be as widely applicable as
possible for real-world programs. Secondly, we strived for a
statistically significant result, reducing the number of variables
present in the experiments. For this reason we chose a random sample
of Java projects from Github\cite{github} that use the popular
maven\cite{maven} build system, following the methodology used by some
of the authors in an ICSE 2014 paper~\cite{gopinath2014code}. As in
that work, we utilize two kinds of of test suites: the original test
suites present in a limited number of projects, and automatically
generated test suites from Randoop~\cite{randoop}.  Due to limited
resources, we had to further reduce the programs and test suites to those
that could finish mutation analysis in 10 minutes. From this set of test
suites, we sampled 110 suites each for both original and Randoop generated
test suites. Since there was some overlap between projects with original
test suites, and those with Randoop test suites, we had 81 unique projects
each in both sets. The remaining projects had both flavors of test suites.
% {\bf ADG I have no idea what that last sentence means, really.
% RG: Fixed}

@@

We next extended this approach to sample from each method instead, but
used the number of lines in the method as the number of mutants to be
sampled from it. This provided a test of the hypothesis of how
important a mutation sampling's relationship to simple code coverage
was. This was extended to class and project scope also.

For the first variant, we applied the x\% sampling to the result of the first
sampling based on line counts. That is, in the case of methods, we first
selected \textit{linecount} mutants each from each method, and applied the x\%
selection to the result of this selection. For e.g for $1/2$ sampling on methods
if a method had $10$ lines and another had $10$ lines, we sampled $10$ mutants
from the first, and $20$ mutants from the second, and from the combined $30$
mutants, we sampled $15$.  For the second variant, we did the sampling in one go,
where we chose \textit{linecount/x} number of mutants from each program element.
That is, in the previous example, only $5$ mutants from the first and $10$ mutants
from the second method would be chosen.

%{\bf ADG:  Could maybe make this clearer?}
% RG: Fixed with an example.
